How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-09-11 research/paper/draft.tex
small updates

\documentclass[12pt, onecolumn]{emulateapj}

@@

\textbf{Obviously I need to write the lit. review!}

This paper aims to answer the following questions:

@@

\textbf{This needs reorganization and clarification.}

@@

\textbf{This needs explication.}

@@

\textbf{I need to write this section!}

@@

\textbf{This test will combine several systematics discussed above.}

We summarize the details of the realistic data here.

@@

>>>>

\documentclass[iop]{emulateapj}

@@

After a brief review of the literature, this paper aims to answer the following 
questions:

@@

@@

@@

@@

The realistic data combines several of the systematic effects of Sec. 
\ref{sec:mockdata}.

@@

\bibliographystyle{apj}
\bibliography{references}
